---
title: "Data Analysis on Worldwide Child Malnutrition"
author: "Jing Cao, Jingjing Dong, Xinyue Sun, Erica Zhang"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
source("../source/aggregate_table.R")
source("../source/summary_info.R")
source("../source/chart1.R")
source("../source/chart2.R")
source("../source/chart3.R")
knitr::opts_chunk$set(echo = FALSE)
```

#### Overall Summarization
```{r summary}
summary_info
```

The project reports current relevant information on child malnutrition from `r summary_info$beginning_year` to `r summary_info$end_year`. To have a more comprehensive analysis, we have `r summary_info$num_observations` observations in total in exploring child malnutrition situations among different regions and how it can be affected by different household incomes. The `r summary_info$num_variables` variables we have for the report are prevalence and number of three different types of malnutrition along with the influential factor region and year. `r pull(summary_info$max_stunting_prev_num_region, region)` has the highest prevalence of stunting, `r max_num`%. `r pull(summary_info$max_overweight_prev_num_region, region)` has the highest prevalence of overweight, and the number is `r max_num2`%. `r pull(summary_info$max_wasting_prev_num_region, region)` also has the highest prevalence of wasting, which is `r max_num3`%.


#### Demonstration of table containing aggregate data
```{r table}
mulnutrition_data
```

This table contains all data on child malnutrition from 2010 to 2020 across various regions provided by UNICEF. Since we want to explore the pattern of child malnutrition, we can access concrete population and prevalence of malnourished kids from this aggregate data. The purpose of this table is not only to allow us to conveniently filter the data for further analysis, but also to enable our audience to understand the scope of this project. In detail, this table reveals annual numbers and percentages of child stunting, overweight, and wasting in each region. We can roughly learn the trend and distribution of child malnutrition from this table. It is noticed that data on child wasting were missing in earlier years. Using `group_by` on the feature `region`, it can be found that there are 12 dimensions, in which one for global, six for WHO regions, and five for World Bank income groups. These dimensions facilitate our analysis on child malnutrition by region and by income.

#### Demonstration of plot one
```{r plot 1}
plot_1
```

This bar plot directly shows the how three mulnutrition types distributed 
in different WHO regions in 2020. The purpose of this plot is to demonstrate
and compare the current prevalence of children suffering from malnutrition 
over different regions which is one of our research questions. As shown in 
the plot, six different regions are counted which are African Region, Region 
of the Americas, South-East Asia Region, Eastern Mediterranean Region, Europe 
Region, and Western Pacific Region. The three types of mulnutrition are overweight, 
stunting, and wasting. The condition in each region is totally different. Except
western pacific region, stunting children occupies the largest percentage of all 
mulnutrition children in other regions for which the percentage of stunting children 
reach the largest among all regions in African Region. In African Region and Region 
of the Americas, the percengate of wasting children is the second large.

#### Demonstration of plot two
```{r plot 2}
chart
```

This run chart shows number of millions of children affected by stunting and overweight globally from 2010 to 2020.
All children suffered from those two malnutrition symptoms are aged under five. 
It is clearly reflected that many more children are affected by stunting over recent ten years. 
The number of overweight children is between 35 to 40 million and is increasing slowly. 
The number of stunting children had reached 180.5 million in year 2010, 
but the negative slope also shows a positive trend that there are fewer children are stunting.
This visualization only shows two symptoms of mulnutrition, 
and the reason of excluding wasting is that we only have data of wasting in 2020. 
Since wasting has not been concerned by the public until recent years, the information we can have is rare. More detailed information about wasting is shown in plot 1 and in aggregated table.   

#### Demonstration of plot three
```{r plot 3}
stunting_plot
overweight_plot
wasting_plot
```

These visualizations were designed to answer one of our research questions, 
how does household income affect child malnutrition? Three pie charts are presented, 
each corresponding to one specific malnutrition type: overweighting, stunting, 
and wasting. These pie charts show the number of malnutrition kids by different income types. 
For overweighting and stunting, the number displayed was the average count 
of malnutrition kids from 2011 to 2020. For wasting, we are showing the malnutrition data for 2020 
since we only have the dataset for that year. One significant insight is that 
low-middle income always has the largest number across all types of malnutrition. 
High income has the lowest number in both stunting and wasting, 
whereas low income has the highest number in overweighting malnutrition.


